Synthesizing Verified Components for Cyber Assured Systems Engineering \thanks{DISTRIBUTION STATEMENT A. Approved for public release.}

### 2022-03-28 paper/high-assurance-contracts.tex
Slight wordsmithing

\subsubsection{Monitor specification}
The monitor policy is given by the \konst{eq}-statements in \linesref{line:mon-assume}{line:mon-policy} of
\figref{fig:monitor}.
\lineref{line:mon-alert}. The \texttt{alert} variable
(distinct from the \texttt{Alert} port) depends not just on the policy
but also on configuration details supplied when the component is
specified.  At configuration time, \texttt{is\_latched} has been set
to \konst{true}, thus making the alert persistent, meaning that once
the alert is raised, it is always raised; otherwise, it is the
complement of the policy value in the current step.

\lineref{line:mon-pre-pending}, \lineref{line:mon-pending}, and \lineref{line:mon-latency}.
The monitor policy is defined by marking when a request is not
satisfied, \texttt{isPending}, and
counting the number of steps between requests, \texttt{latency}.  
The \texttt{isPending} variable is true
whenever there is a request that does not coincide with a
response--to be read as \emph{there is no response since the most recent request without a corresponding response}.  The
\texttt{latency} variable starts at zero, resets on every request, and
otherwise increments by one. 
The \texttt{preIsPending} is needed to make the contract Pascalish since since the current and previous value of \texttt{isPending} are used in the definition of \texttt{policy}.

\lineref{line:mon-policy}. 
The policy makes sure the latency is bounded whenever there is a pending request, and it it makes sure that a response is a result of a request.
The initial step differentiates from later steps in only needing to be sure a response is a result of a request.

\lineref{line:mon-const}. The latency bound for the monitor is defined by the constant
\texttt{MAX\_LATENCY}.  Here the constant
is set to one to be consistent with the system specification from the
previous section.  At time zero the policy is trivial: a response
requires an accompanying request.  After time zero, if a request is
pending in the current time step, then the latency must still be under
the bound, and if there is a response, then it closes a request now or
a pending request from earlier in time.

\lineref{line:mon-assume}. The policy definition only works if there is never more than one
outstanding request at a time; otherwise, the latency counter resets
incorrectly.  That requirement is encoded in the assumption and is the same assumption used for the
system input.  The policy can be written without the assumption,
but the policy is much simpler to write with the assumption.

>>>>

\subsubsection{Monitor specification}
The monitor policy is given by the \konst{eq}-statements in \linesref{line:mon-assume}{line:mon-policy} of
\figref{fig:monitor}.
\lineref{line:mon-alert}: The \texttt{alert} variable
(distinct from the \texttt{Alert} port) depends not just on the policy
but also on configuration details supplied when the component is
specified.  At configuration time, \texttt{is\_latched} has been set
to \konst{true}, thus making the alert persistent, meaning that once
the alert is raised, it is always raised; otherwise, it is the
complement of the policy value in the current step.

\lineref{line:mon-pre-pending}, \lineref{line:mon-pending}, and \lineref{line:mon-latency}:
The monitor policy is defined by marking when a request is not
satisfied, \texttt{isPending}, and
counting the number of steps between requests, \texttt{latency}.  
The \texttt{isPending} variable is true
whenever there is a request that does not coincide with a
response--to be read as \emph{there is no response since the most recent request without a corresponding response}.  The
\texttt{latency} variable starts at zero, resets on every request, and
otherwise increments by one. 
The \texttt{preIsPending} is needed to make the contract Pascalish since since the current and previous value of \texttt{isPending} are used in the definition of \texttt{policy}.

\lineref{line:mon-policy}: 
The policy makes sure the latency is bounded whenever there is a pending request, and it it makes sure that a response is a result of a request.
The initial step differentiates from later steps in only needing to be sure a response is a result of a request.

\lineref{line:mon-const}: The latency bound for the monitor is defined by the constant
\texttt{MAX\_LATENCY}.  Here the constant
is set to one to be consistent with the system specification from the
previous section.  At time zero the policy is trivial: a response
requires an accompanying request.  After time zero, if a request is
pending in the current time step, then the latency must still be under
the bound, and if there is a response, then it closes a request now or
a pending request from earlier in time.

\lineref{line:mon-assume}: The policy definition only works if there is never more than one
outstanding request at a time; otherwise, the latency counter resets
incorrectly.  That requirement is encoded in the assumption and is the same assumption used for the
system input.  The policy can be written without the assumption,
but the policy is much simpler to write with the assumption.

### 2022-03-28 paper/testing.tex
Slight wordsmithing

\figref{fig:test} is a unit test for the high-assurance monitor in \figref{fig:hardened}.
The test checks if the monitor output coincides with the response that comes one step after the request.
It also checks that the alarm does not fire.
\begin{compactitem}
\item \lineref{line:tst-index}. An index to use to define the test input and expected test output through time.
\item \lineref{line:tst-assume-1} and \lineref{line:tst-assume-2}. The test input. These define when the request and response message events should appear relative to the index.
\item \lineref{line:tst-guarantee-1} and \lineref{line:tst-guarantee-2}. The expected test output. 
The test additionally proves that nothing happens after the initial test input and expected output, \ie, no more input is provided and no more output is generated.
\item \linesref{line:tst-imp-start}{line:tst-imp-end}. The implementation with the component under test (\lineref{line:tst-imp-comp}).
\end{compactitem}
\figref{fig:test-output} is the AGREE output for the test, showing that it passes.

>>>>

\figref{fig:test} is a unit test for the high-assurance monitor in \figref{fig:hardened}.
The test checks if the monitor output coincides with the response that comes one step after the request.
It also checks that the alarm does not fire.
\begin{compactitem}
\item \lineref{line:tst-index}: An index to use to define the test input and expected test output through time.
\item \lineref{line:tst-assume-1} and \lineref{line:tst-assume-2}: The test input. These define when the request and response message events should appear relative to the index.
\item \lineref{line:tst-guarantee-1} and \lineref{line:tst-guarantee-2}: The expected test output. 
The test additionally proves that nothing happens after the initial test input and expected output, \ie, no more input is provided and no more output is generated.
\item \linesref{line:tst-imp-start}{line:tst-imp-end}: The implementation with the component under test (\lineref{line:tst-imp-comp}).
\end{compactitem}
\figref{fig:test-output} is the AGREE output for the test, showing that it passes.
